---
title: "WearCPS: Safety vs. Security Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("Data.Rdata")

library(ggplot2)
```

## Introduction

Below is the initial analyis/breakdown of the test data collected through our website **WearCPS.me**.

## Average Ages

Average ages of participants:

```{r analysis, incude=TRUE}

summary(Ages$age)

ggplot(Ages, aes(x=age)) +  geom_dotplot(binwidth = .3) +
  scale_y_continuous(name = "", breaks = NULL) + ggtitle("Average Ages") +
  labs(x="Ages",y="Ages") 
```

## Avg. Score

Basic plot of Avg. Score:

```{r analysis2, incude=TRUE}

summary(SexVsScore)

ggplot(SexVsScore, aes(x=finalScore)) +  geom_density(kernel = "gaussian", fill='orange') + ggtitle("Avg. Score") + labs(x="Score", y ="Density") 
```

## Avg. Response Time

Basic plot of Avg. Response Times:

```{r analysis3, incude=TRUE}

summary(NotificationResponseTimes)

x <- data.frame(v1=NotificationResponseTimes$avg,v2=NotificationResponseTimes$secAvg,v3=NotificationResponseTimes$safAvg)
library(ggplot2);library(reshape2)
data<- melt(x)
ggplot(data,aes(x=value, fill=variable)) + geom_density(alpha=0.25) + ggtitle("Response Times") + labs(x="Time(ms)", y ="Density")
```

## Recall Correctness

Basic plot of Recall Correctness:

```{r analysis4, incude=TRUE}

summary(RecallCorrectPercentages)

```
**Note** that the `echo = FALSE` parameter can be added to the code chunk to prevent printing of the R code that generates the plot.
